---
title: "aptsalesprocessing"
author: "Emanuel Pizana"
date: "10/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

``````{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(data.table)
library(ggplot2)
library(RColorBrewer)
library(plotly)
library(shiny)
library(shinydashboard)
```


#load csv
```{r load_data, cache=TRUE, warning=TRUE, message=FALSE}
loadcolumns = 'iccfciiiiifciDifffiiccc'
combined = read_csv('combined.csv', col_names = TRUE, col_types = loadcolumns)
combined = as.data.frame(combined, row.names = combined$Index)
rownames(combined) = combined$Index
combined$Index = NULL
colnames(combined) = tolower(colnames(combined))
colnames(combined) = gsub(' ','.',colnames(combined))

head(combined)
dim(combined)


building_sales = read_csv('buildsales.csv', col_names = TRUE, col_types = loadcolumns)
building_sales = as.data.frame(building_sales, row.names = building_sales$Index)
rownames(building_sales) = building_sales$Index
building_sales$Index = NULL
head(building_sales)
dim(building_sales)

aptsales = read_csv('aptsales.csv', col_names = TRUE, col_types = loadcolumns)
aptsales = as.data.frame(aptsales, row.names = aptsales$Index)
#aptsales$Index = NULL
rownames(aptsales) = aptsales$Index
aptsales$Index = NULL
head(aptsales)
dim(aptsales)

colnames(combined)
```

## Manipulation


```{r}


####ALL TRANSACTIONS#######


totalNYC = combined %>% group_by(.,sale.year) %>% summarise(., mean_price = mean((sale.price)))


coopNYC = combined %>% filter(., type == 'Co-op', construction == 'Pre-prewar') %>% group_by(.,sale.year) %>% summarise(., mean_price = mean((sale.price)))


plot_ly(coopNYC, x = ~sale.year, y = ~mean_price, type = 'scatter', mode = 'lines') %>% 
                    layout(title = "Average Price Over Time",
                    xaxis = list(title = 'Sale Year'),
                    yaxis = list(title = 'Average Price $'))


plot_ly(totalNYC, x = ~sale.year, y = ~mean_price, type = 'scatter', mode = 'lines') %>% 
                    layout(title = "Average Price Over Time",
                    xaxis = list(title = 'Sale Year'),
                    yaxis = list(title = 'Average Price $'))


 

  


###+++Apt Sales is filtered for ALL RESIDENTIAL BUILDINGS
#WITH MULTIPLE TRANSACTIONS. USED FOR UNIT PRICE ANALYSIS, and BUILDING ANALYSIS, down below!+++###

aptsales1 = combined[duplicated(combined$main_address) | duplicated(combined$main_address, fromLast = TRUE), ] %>% filter(., !is.na(apt_no)) %>% arrange(., main_address, sale.price)

dim(aptsales1)
summary(aptsales1)


# ++++++count and average price of buildings only +++++++++++
avg_price_building = combined[duplicated(combined$building_address) | duplicated(combined$building_address, fromLast = TRUE), ] %>% group_by(.,building_address) %>% summarise(.,avg_price = mean(sale.price)) %>% arrange(., desc(avg_price))
  
building_counts = combined[duplicated(combined$building_address) | duplicated(combined$building_address, fromLast = TRUE), ] %>% group_by(.,building_address) %>% summarise(., num_sold = n()) %>% arrange(., desc(num_sold))

building_counts_price = inner_join(building_counts,avg_price_building, by='building_address') 


#++++++++CONDOS ONLY WITH MULTIPLE SALES, FROM aptsales1 +++++++++

#master file filtered for condos.
condosales = aptsales1 %>% filter(., type == 'Condo')



#main_address counts in desc order
condobycount = condosales %>% group_by(.,main_address) %>% summarise(.,condosalescount = n()) %>% arrange(., desc(condosalescount))
condobycount

#grouped by sales dates
condobydate = condosales %>% group_by(., main_address, sale.date) %>%
  arrange(.,main_address, sale.date)

condobydate

#+++$$$$$$$$$$++++++++P&L by condo++++++$$$$$$$$$$$$$$

#use data.table to set up P&L view 
condopl = as.data.table(condobydate)
setnames(condopl, old = c("sale.date", "sale.price", "sale.year"), new = c('purchase.date',"purchase.price","purchase.year"))

condopl[, sell_date:=shift(purchase.date, 1, type='lead'), by=main_address]
condopl[, sell_price:=shift(purchase.price, 1, type='lead'), by=main_address]
condopl[, sale_year:=shift(purchase.year, 1, type='lead'), by=main_address]

#fill na sell_price with 0s
condopl[is.na(sell_price), sell_price := 0]

#calculate P&L, exclude properties still held by buyer, and determine holding period
condopl = as.data.frame(condopl)
condopl = condopl %>% filter(., sell_price != 0) %>% mutate(., price_change = sell_price - purchase.price, days = as.numeric(sell_date - purchase.date), hldg_return = (price_change/purchase.price))

#there are extreme negative outliers with price change, due to
#listings that purchase the entire building attributed to a single
#apartment. Also, some transactions are bought and sold within a span of zero days or within 60 days. Take these out.

plmin = quantile(condopl$price_change, 0.0005)
condopl = condopl %>% filter(., price_change > plmin, days >= 60)

condopl %>% ggplot () +
  geom_density(aes(x = days, fill = borough, alpha = .05))

#dim(aptsales1)
#summary(aptsales1)

condobydate

condosales %>% filter(., main_address == '25 MURRAY STREET, 2D') %>% arrange(., sale.date)

combined %>% filter(., grepl("170 EAST END",main_address))

condopl

```

```{r}


((1.0348837*1.0898876)^(365/(2082+448)))-1
1

condopl = condopl %>% filter(., days > 365) %>% mutate(., rtrn_factor = hldg_return + 1) #%>% group_by(., main_address) %>% summarise(.,total_days = sum(days))

#filter for holding periods of at least a year
testdays = condopl %>% filter(., days > 365) %>% group_by(., main_address) %>% summarise(.,total_days = sum(days))

testmultreturns = condopl %>% group_by(., main_address) %>% mutate(., prdrtrns = prod(rtrn_factor)) %>% select(., main_address, prdrtrns) %>% unique()
testmultreturns

testdaysreturns = inner_join(testmultreturns, testdays, by = 'main_address')

testdaysreturns = testdaysreturns %>% mutate(., annual_return = round(((prdrtrns^(365/total_days))-1),3)) %>% arrange(., desc(annual_return))
testdaysreturns

testdaysreturns$prdrtrns = NULL

forgraph = testdaysreturns
forgraph = forgraph %>% select(., main_address, total_days, annual_return)
forgraph

colnames(condopl)



# lenmult = dim(testmultreturns)[1]
# lendays = dim(testdays)[1]
# 
# lenmult == lendays


  



condopl %>% filter(., main_address == '88 FRANKLIN STREET, PH')

basics = combined %>% select(., main_address, building_address, borough, neighborhood, current.age, type, construction, year.built) %>% unique() %>% arrange(., main_address)

basics

testjoin = left_join(forgraph,basics, by = 'main_address')
testjoin

```

```{r}

condosales %>% group_by(.,sale.year) %>% summarise(., mean_price = mean((sale.price))) %>%
    plot_ly(., x = ~sale.year, y = ~mean_price, type = 'scatter', mode = 'lines') %>% 
      layout(title = "Average Price Over Time",
             xaxis = list(title = 'Sale Year'),
             yaxis = list(title = 'Average Price $'))
 
condosales %>% group_by(.,sale.year) %>% filter(., sale.year == 2018) #summarise(., mean_price = mean((sale.price)))


aptsales1 = combined[duplicated(combined$main_address) | duplicated(combined$main_address, fromLast = TRUE), ] %>% filter(., !is.na(apt_no)) %>% arrange(., main_address, sale.price)


adtest = combined %>% arrange(.,main_address)

adtest1 = adtest[duplicated(adtest$main_address) | duplicated(adtest$main_address, fromLast = TRUE), ]

adtest %>% filter(., grepl("170 EAST END",main_address)) %>% mutate(., x = dense_rank(main_address)) %>%  arrange(., main_address)



```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r testing, echo=FALSE}

age=c(18,18,18, 19, 20, 21, 30, 30, 30, 21, 21, 21)
height=c(76.1,76.1,76.1,78.2,78.8,79.7,79.9,79.9,81.2,81.8,82.8,83.5)
Names=c("John","John","John", "Harry", "Paul", "Paul", "Paul", "Paul", "Khan", "Khan", "Sam", "Joe")
village <- data.frame(Names, age, height)
village

village[duplicated(village) | duplicated(village, fromLast = TRUE), ]

prod(c(1,2,4,5))
```